---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dialektversum

<!-- badges: start -->
<!-- badges: end -->

The goal of `dialektversum` is to provide access to various packages that translate German to German dialects. 

## Installation

You can install the development version of `dialektversum` from GitHub with:

``` r
#install.packages("remotes")
remotes::install_github("favstats/dialektversum")
```


```{r example}
library(dialektversum)

```


Currently `dialektversum` supports full-text translations into **7 German dialects**. They are:

## Swabian with [`schwabr`](https://github.com/favstats/schwabr)

```{r}
get_schwab("Widerrechtlich abgestellte Fahrzeuge werden kostenpflichtig abgeschleppt.")
```

## Plattdeutsch with [`plattdeutschr`](https://github.com/favstats/plattdeutschr)

```{r}
get_plattdeutsch("Widerrechtlich abgestellte Fahrzeuge werden kostenpflichtig abgeschleppt.")
```

## Bavarian with [`bayeRisch`](https://github.com/favstats/bayeRisch)

```{r}
get_bayerisch("Widerrechtlich abgestellte Fahrzeuge werden kostenpflichtig abgeschleppt.")
```

## Hessian with [`hessr`](https://github.com/favstats/hessr)

```{r}
get_hessisch("Widerrechtlich abgestellte Fahrzeuge werden kostenpflichtig abgeschleppt.")
```

## Saxonian with [`sachsr`](https://github.com/favstats/sachsr)

```{r}
get_saxonian("Widerrechtlich abgestellte Fahrzeuge werden kostenpflichtig abgeschleppt.")
```

## Berlin dialect with [`berlinr`](https://github.com/favstats/berlinr)

```{r}
get_berlinerisch("Widerrechtlich abgestellte Fahrzeuge werden kostenpflichtig abgeschleppt.")
```







